### 2017-10-11 Sections/a_new_frontier_towards_the_singularity.tex

We acknowledge that while parts of these essays are highly plausible, if not certain, others are highly speculative, but nonetheless based on believable although somewhat futuristic reasoning.

>>>>

We acknowledge that while parts of these essays are highly plausible, if not certain, others are highly speculative, but nonetheless based on believable although somewhat futuristic reasoning. At the very least we hope to stimulate the exchange of ideas and their development. We encourage the reader to question the ideas presented in these essays and put forth their own ideas and predictions.

\textit{``There is no harm in doubt and skepticism, for it is through these that new discoveries are made.''} --- Richard Feynman.

### 2017-10-11 Sections/costs_and_attributes_in_quantum_networks.tex
minor
Fusion gates fig. Stubs for fusion strategies

\section{Cost vector analysis} \label{sec:quantum_meas_cost}
\index{Costs}\index{Attributes}\index{Cost vector analysis}
\comment{Use term 'cost vector analysis' all over the place}
As with the classical case in Sec.~\ref{sec:costs}, there will be costs associated with the links and nodes in a network -- nothing is free! In the quantum case, all the usual classical costs are valid, but there are some very important additions of far greater relevance to most quantum applications. Classical digital data is discretised, resulting in data transmission highly robust against noise. In a quantum setting this is necessarily not the case, as the coefficients in quantum superpositions are continuous, meaning that errors accumulate during transmission and states will inevitably deteriorate, unlike digital states. This requires a rethinking of appropriate cost metrics.

@@

The measures considered until now have quantified the preservation of quantum states. Alternately, one might consider information theoretic measures, which quantify the number of bits/qubits transmitted by a link, i.e the number of bits/qubits in common before and after the channel. This is an extremely powerful tool as it upper bounds the amount of information the receiver can extract from the transmitter under \textit{any} measurement scheme, very useful in a cryptographic context, where we want security to be attack-independent.

@@

If we consider a lossy photonic channel for example, efficiencies ($\eta$) are multiplicative -- for a route \mbox{$v_1\to v_2\to v_3$}, the net efficiency is given by the product of the individual efficiencies, \begin{align}
\eta_{v_1\to v_2 \to v_3} = \eta_{v_1\to v_2} \eta_{v_2\to v_3}.
\end{align}
This is multiplicative rather than additive, clearly not satisfying our definition for a cost metric. However, multiplicative metrics such as this can easily be made additive by shifting to a logarithmic scale, since
\begin{align}
\log(\eta_{v_1\to v_2\to v_3}) = \log(\eta_{v_1\to v_2}) + \log(\eta_{v_2\to v_3}),
\end{align}
which now has a legitimate interpretation as a distance. The same applies to, for example, frequency response functions, which are equivalent to frequency-dependent loss.

In general, for a series of links \mbox{$v_1\to v_2 \to \dots \to v_n$} characterised by multiplicative measure $m$, the equivalent cost metric is,
\begin{align} \label{eq:dist_log}
c_{v_1\to v_2 \to \dots \to v_n} = -\sum_{i=1}^{n-1} \text{log}(m_{v_i\to v_{i+1}}).
\end{align}
We have assumed that \mbox{$0\leq m \leq 1$}, where \mbox{$m=0$} represents complete failure, and \mbox{$m=1$} represents ideal operation.

>>>>

\section{Quantum cost vector analysis} \label{sec:quantum_meas_cost}
\index{Costs}\index{Attributes}\index{Cost vector analysis}

\comment{Use term 'cost vector analysis' all over the place}
As with the classical case in Sec.~\ref{sec:costs}, there will be costs associated with the links and nodes in a network -- nothing is free! In the quantum case, all the usual classical costs are valid, but there are some very important additions of far greater relevance to most quantum applications. Classical digital data is discretised, resulting in data transmission highly robust against noise. In a quantum setting this is necessarily not the case, as the coefficients in quantum superpositions are continuous, meaning that errors accumulate during transmission and states will inevitably deteriorate, unlike digital states. This requires a rethinking of appropriate cost metrics.

@@

The measures considered until now have quantified the preservation of quantum states. Alternately, one might consider information theoretic measures, which quantify the number of bits/qubits transmitted by a link, i.e the number of bits/qubits in common before and after the channel. This is an extremely powerful tool as it upper bounds the amount of information the receiver can extract from the transmitter under \textit{any} measurement scheme, very useful in a cryptographic context, where we want security to be attack-independent\index{Attack-independence}.

@@

If we consider a lossy photonic channel for example, efficiencies ($\eta$) are multiplicative -- for a route \mbox{$v_1\to v_2\to v_3$}, the net efficiency is given by the product of the individual efficiencies, \begin{align}
\eta_{v_1\to v_2 \to v_3} = \eta_{v_1\to v_2} \eta_{v_2\to v_3}.
\end{align}
This is multiplicative rather than additive, clearly not satisfying our definition for a cost metric. However, multiplicative metrics\index{Multiplicative metrics} such as this can easily be made additive\index{Additive metrics} by shifting to a logarithmic scale, since
\begin{align}\index{Logarithmic scale}
\log(\eta_{v_1\to v_2\to v_3}) = \log(\eta_{v_1\to v_2}) + \log(\eta_{v_2\to v_3}),
\end{align}
which now has a legitimate interpretation as a distance. The same applies to, for example, frequency response functions, which are equivalent to frequency-dependent loss.

In general, for a series of links \mbox{$v_1\to v_2 \to \dots \to v_n$} characterised by multiplicative measure $m$, the equivalent cost metric is,
\begin{align} \label{eq:dist_log}\index{Logarithmic distance}
c_{v_1\to v_2 \to \dots \to v_n} = -\sum_{i=1}^{n-1} \text{log}(m_{v_i\to v_{i+1}}).
\end{align}
We have assumed that \mbox{$0\leq m \leq 1$}, where \mbox{$m=0$} represents complete failure, and \mbox{$m=1$} represents ideal operation.

### 2017-10-11 Sections/economics_of_the_quantum_internet.tex

The exact form of the scaling function will be specific to the algorithm being deployed\footnote{For example, the \textit{circuit depth}, i.e number of gate applications in series, will heavily influence the number of classical steps required to simulate the circuit.}, and the computational model (e.g cluster states vs the circuit model, as well as choices in error correction, amongst other factors). Most notably, different quantum algorithms offer different scalings in their quantum speedup -- Grover's algorithm offers only a quadratic quantum speedup, compared to the exponential speedup afforded by Shor's algorithm. Thus, the computational scaling function depends on both the hardware and software.

%
% Virtual Scaling Functionx
%

@@

This is a reasonable assumption based on the observation of this ubiquitous kind of behaviour in present-day technologies. Classical computing has been on an exponential trajectory since the 1980's, and although it must eventually asymptote, it shows no sign of doing so in the immediate future. Quantum technologies sit at the entry point tox this trajectory, and we expect it to continue for the medium-term. Thus, we let the number of qubits in the network be,
\begin{postulate}[Network growth]\label{post:net_growth}\index{Network growth postulate}
The number of qubits in the global quantum internet is growing exponentially over time as,
\begin{align}
	N_t = N_0 {\gamma_N}^{t},
\end{align}
where \mbox{$\gamma_N\geq 1$} characterises the rate of exponential growth in the number of qubits available to the quantum network.
\end{postulate}

@@

The total computational power of the entire network now scales as,
\begin{align}
n_\text{FLOPS}(t) = f_\text{sc}(N_0{\gamma_N}^t),
\end{align}
based on the network growth postulate (Pos.~\ref{post:net_growth})\index{Network growth postulate} and employing a combined computational scaling function\index{Combined computational scaling function} (Def.~\ref{def:comb_sc_func}). The dollar-value of current net computational power of the entire network scales as,
\begin{align}
	n_\text{gain}(t) &= N_t L_t \cdot n_\text{FLOPS}(t) \nonumber \\
	&= N_0 {\gamma_N}^t L_t\cdot f_\text{sc}(N_0 {\gamma_N}^t).
\end{align}
And the present-day dollar-value of the physical hardware is the product of the hardware cost per qubit and the number of qubits,
\begin{align}
	n_\text{invest}(t) &= N_t C_t \nonumber \\
	&= N_0 C_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t.
\end{align}
Equating these, as per Eq.~(\ref{sec:gain_eq_invest}), yields,
\begin{align}
N_0 {\gamma_N}^t L_t\cdot f_\text{sc}(N_0 {\gamma_N}^t) \gtrapprox N_0 C_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t,
\end{align}
which yields the time-depenent cost of computation postulate,

@@

\subsubsection{The quantum stockmarket}\index{Quantum stockmarket}

@@

This effetively implies that some users pay more for computation (in terms of RoI\index{Return on investment}) than others. While the objective cost of computation is conceptually simple to model (as performed in a rudimentary fashion in Sec.~\ref{sec:cost_of_comp}), the subjective cost is a highly non-trivial one. It will depend heavily on the scaling function of the algorithm run by a user, and of course the economic objectives of their computation -- a quantum simulation algorithm executed by an R\&D lab\index{R\&D} is likely to be of greater monetary value than and undergrad using his university's resources for completing an assignment.

The question then is how to reconcile the distinction between subjective and objective value, given the diversity of applications in the quantum marketplace. This will supercede the na\"ive models for cost of computation presented earlier, which were based entirely on objective value. Of course, subjective value is what people are actually willing to pay for in the real-world!

This will give rise to a marketplace for tradeable units of quantum computation, where the underlying asset is time-shares in the global network. We refer to this as the \textit{quantum stockmarket} -- a marketplace subject to ordinary supply and demand, economic, and psychological pressures. In a scenario where a large number of users are executing computations with high return (think the R\&D lab), asset values will be traded up. Contrarily, in a scenario of low-return computations (think our poor undergrad), they will be traded down. These market forces will be highly time-dependent, varying against many other factors in the economy, such as the emergence of new applications for quantum computing.

The relative market value of computation will subsequently drive the direction of investment into quantum hardware, with carry-over effects on future market prices. If investment stagnates, so too will growth in computational dividends, driving up market rates by limiting supply (assuming positive growth in demand). This will, after market adjustment, drive investment back into the system to satisfy increasing demand. Thus, despite the present uncertainty into the future dynamics of the quantum stockmarket, we expect this positive feedback loop to ensure consistent, ongoing investment into the network, and at least some marginal degree of price stability.

What is likely to arise is that most owners of quantum hardware will not be consumers, but rather investors, who float their resources on the quantum stockmarket, betting on changes in demand for computation and their associated subjective cost. For example, an investor anticipating a surge in high-value computations is likely to invest more heavily into hardware with the expectation of an uptrend in market rates. And their RoI will reflect these market dynamics.

As all markets for tradeable assets do, sophisticated derivative markets will inevitably emerge, whereby people can speculate on or hedge against market dynamics, taking long, short, or more complex market positions, potentially in a highly-leveraged manner. As discussed in Sec.~\ref{sec:for_contr}, derivatives such as future contracts can be extremely helpful in enabling consumers to lock in future prices, creating a stable business climate. Similarly, other derivatives will enable market participants to hedge\index{Hedging} other quantum-related investments. For example, suppose an investor held a stake in an R\&D lab, highly reliant on quantum computing. By taking a leveraged long position on the market value for computation, he may limit losses on his R\&D investment associated with the higher price (and hence lower profit) they will be paying for computation.

>>>>

The exact form of the scaling function will be specific to the algorithm being deployed\footnote{For example, the \textit{circuit depth}, i.e number of gate applications in series, will heavily influence the number of classical steps required to simulate the circuit.}, and the computational model (e.g cluster states vs the circuit model, as well as choices in error correction, amongst other factors). Most notably, different quantum algorithms offer different scalings in their quantum speedup -- Grover's algorithm offers only a quadratic quantum speedup, compared to the exponential speedup afforded by Shor's algorithm\index{Shor's algorithm}. Thus, the computational scaling function depends on both the hardware and software.

%
% Virtual Scaling Functions
%

@@

This is a reasonable assumption based on the observation of this ubiquitous kind of behaviour in present-day technologies. Classical computing has been on an exponential trajectory since the 1980's, and although it must eventually asymptote, it shows no sign of doing so in the immediate future. Quantum technologies sit at the entry point to this trajectory, and we expect it to continue for the medium-term. Thus, we let the number of qubits in the network be,
\begin{postulate}[Network growth]\label{post:net_growth}\index{Network growth postulate}
The number of qubits in the global quantum internet is growing exponentially over time as,
\begin{align}
	N_t = N_0 {\gamma_N}^{t},
\end{align}
where \mbox{$\gamma_N\geq 1$} characterises the rate of exponential growth in the number of qubits available to the quantum network.
\end{postulate}

@@

The total computational power of the entire network now scales as,
\begin{align}
n_\text{FLOPS}(t) = f_\text{sc}(N_0{\gamma_N}^t),
\end{align}
based on the network growth postulate (Pos.~\ref{post:net_growth})\index{Network growth postulate} and employing a combined computational scaling function\index{Combined computational scaling function} (Def.~\ref{def:comb_sc_func}). The dollar-value of current net computational power of the entire network scales as,
\begin{align}
	n_\text{gain}(t) &= N_t L_t \cdot n_\text{FLOPS}(t) \nonumber \\
	&= N_0 {\gamma_N}^t L_t\cdot f_\text{sc}(N_0 {\gamma_N}^t).
\end{align}
And the present-day dollar-value of the physical hardware is the product of the hardware cost per qubit and the number of qubits,
\begin{align}
	n_\text{invest}(t) &= N_t C_t \nonumber \\
	&= N_0 C_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t.
\end{align}
Equating these, as per Eq.~(\ref{sec:gain_eq_invest}), yields,
\begin{align}
N_0 {\gamma_N}^t L_t\cdot f_\text{sc}(N_0 {\gamma_N}^t) \gtrapprox N_0 C_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t,
\end{align}
which yields the time-dependent cost of computation postulate,

@@

\subsubsection{The quantum stock market}\index{Quantum stock market}

@@

This effectively implies that some users pay more for computation (in terms of RoI\index{Return on investment}) than others. While the objective cost of computation is conceptually simple to model (as performed in a rudimentary fashion in Sec.~\ref{sec:cost_of_comp}), the subjective cost is a highly non-trivial one. It will depend heavily on the scaling function of the algorithm run by a user, and of course the economic objectives of their computation -- a quantum simulation algorithm executed by an R\&D lab\index{R\&D} is likely to be of greater monetary value than and undergrad using his university's resources for completing an assignment!

The question then is how to reconcile the distinction between subjective and objective value, given the diversity of applications in the quantum marketplace. This will supersede the na\"ive models for cost of computation presented earlier, which were based entirely on objective value. Of course, subjective value is what people are actually willing to pay for in the real-world!

This will give rise to a marketplace for tradable units of quantum computation, where the underlying asset is time-shares in the global network. We refer to this as the \textit{quantum stock market} -- a marketplace subject to ordinary supply and demand, economic, and psychological pressures. In a scenario where a large number of users are executing computations with high return (think the R\&D lab), asset values will be traded up. Contrarily, in a scenario of low-return computations (think our poor undergrad), they will be traded down. These market forces will be highly time-dependent, varying against many other factors in the economy, such as the emergence of new applications for quantum computation.

The relative market value of computation will subsequently drive the direction of investment into quantum hardware, with carry-over effects on future market prices. If investment stagnates, so too will growth in computational dividends, driving up market rates by limiting supply (assuming positive growth in demand). This will, after market adjustment, drive investment back into the system to satisfy increasing demand. Thus, despite the present uncertainty into the future dynamics of the quantum stock market, we expect this positive feedback loop to ensure consistent, ongoing investment into the network, and at least some marginal degree of price stability.

What is likely to arise is that most owners of quantum hardware will not be consumers, but rather investors, who float their resources on the quantum stock market, betting on changes in demand for computation and their associated subjective cost. For example, an investor anticipating a surge in high-value computations is likely to invest more heavily into hardware with the expectation of an uptrend in market rates. And their RoI will reflect these market dynamics.

As all markets for tradable assets do, sophisticated derivative markets will inevitably emerge, whereby people can speculate on or hedge against market dynamics, taking long, short, or more complex market positions, potentially in a highly-leveraged manner. As discussed in Sec.~\ref{sec:for_contr}, derivatives such as future contracts can be extremely helpful in enabling consumers to lock in future prices, creating a stable business climate. Similarly, other derivatives will enable market participants to hedge\index{Hedging} other quantum-related investments. For example, suppose an investor held a stake in an R\&D lab, highly reliant on quantum computing resources. By taking a leveraged long position on the market value for computation, he may limit losses on his R\&D investment associated with the higher price (and hence lower profit) they will be paying for computation.

### 2017-10-11 Sections/entanglement_the_ultimate_quantum_resource.tex

What's the advantage of this approach to quantum networking? There are several:
\begin{itemize}
\item Dedicated servers can specialise in this one particular task, as can be the transmission infrastructure. The server needn't concern itself with the nitty-gritty of the protocols implemented by the end-user.
\item Because servers are providing a single standardised product, they can be commodified, enabling mass production of the hardware devices and the associated economy of scale.
\item Unlike generic quantum states, Bell-pairs are known states that can be infinitely reproduced, without having to worry about no-cloning limitations.
\item Photonic Bell-pairs are easily prepared via type-II SPDC at very high repetition rates (\mbox{$\sim 100$MHz-1GHz}), enabling rapid state preparation.
\item Bell-pairs are relatively `cheap' to prepare, and can be readily manufactured using widely accessible, present-day technology.
\item QoS is a lesser issue in most scenarios. We can employ a \textsc{Send and Forget}\index{Send and forget protocol} protocol for the distribution of entanglement (much like classical UDP). Since every Bell-pair is identical, we needn't be concerned about missing ones. Instead, we can simply wait for the next one (a \textsc{Repeat Until Success}\index{Repeat until success strategy} strategy), knowing it will be exactly the same. We call this the \textsc{Shotgun}\index{Shotgun state preparation} approach -- keep firing away until we hit something.
\item Rather than transmitting quantum states between distant parties directly, if we instead use state teleportation, the state to be transmitted will not be corrupted if the communications channel fails (e.g via loss). Instead we can wait for the next successfully transmitted Bell-pair until we are ready to teleport the state, which then proceeds without directly utilising the quantum communications channel, accumulating its associated costs, or risking losing the state altogether should link failure occur. Only classical communication is required to complete the protocol, which can be regarded as error-free for all intents and purposes.
\item Entanglement purification may be employed by the two parties to improve the cost metrics associated with their shared entanglement, thereby partially overcoming the limitations imposed by the quantum communication channels.
\item If no direct link exists between server and clients, bootstrapped entanglement swapping can be employed to concatenate servers to create longer-distance `virtual' links. This is the basis for \textit{quantum repeater networks}, to be discussed next in Sec.~\ref{sec:rep_net}.
\end{itemize}

>>>>

What's the advantage of this approach to quantum networking? There are several:
\begin{itemize}
\item Dedicated servers can specialise in this one particular task, as can be the transmission infrastructure. The server needn't concern itself with the nitty-gritty of the protocols implemented by the end-user.
\item Because servers are providing a single standardised product, they can be commodified, enabling mass production of the hardware devices and the associated economy of scale.
\item Unlike generic quantum states, Bell-pairs are known states that can be infinitely reproduced, without having to worry about no-cloning limitations.
\item Photonic Bell-pairs are easily prepared via type-II SPDC at very high repetition rates (\mbox{$\sim 100$MHz-1GHz}), enabling rapid state preparation.
\item Bell-pairs are relatively `cheap' to prepare, and can be readily manufactured using widely accessible, present-day technology.
\item QoS is a lesser issue in most scenarios. We can employ a \textsc{Send-and-forget}\index{Send-and-forget strategy} protocol for the distribution of entanglement (much like classical UDP). Since every Bell-pair is identical, we needn't be concerned about missing ones. Instead, we can simply wait for the next one (a \textsc{Repeat-until-success}\index{Repeat-until-success strategy} strategy), knowing it will be exactly the same. We call this the \textsc{Shotgun}\index{Shotgun state preparation} approach -- keep firing away until we hit something.
\item Rather than transmitting quantum states between distant parties directly, if we instead use state teleportation, the state to be transmitted will not be corrupted if the communications channel fails (e.g via loss). Instead we can wait for the next successfully transmitted Bell-pair until we are ready to teleport the state, which then proceeds without directly utilising the quantum communications channel, accumulating its associated costs, or risking losing the state altogether should link failure occur. Only classical communication is required to complete the protocol, which can be regarded as error-free for all intents and purposes.
\item Entanglement purification may be employed by the two parties to improve the cost metrics associated with their shared entanglement, thereby partially overcoming the limitations imposed by the quantum communication channels.
\item If no direct link exists between server and clients, bootstrapped entanglement swapping can be employed to concatenate servers to create longer-distance `virtual' links. This is the basis for \textit{quantum repeater networks}, to be discussed next in Sec.~\ref{sec:rep_net}.
\end{itemize}

### 2017-10-11 Sections/multi_packet_operations.tex

To accommodate such multi-packet operations, we must add some modifications to the QTCP protocol to handle:
\begin{itemize}
	\item Packet synchronisation\index{Packet synchronisation}: multiple packets subject to joint operations must be time-synchronised upon implementation of the joint operation. This might involve holding one packet in a quantum memory whilst waiting upon another. Thus, the time required to implement the joint operation is bottlenecked by the packet slowest to arrive.
	\item Bookkeeping of costs and attributes\index{Combining cost \& attributes}: when multiple packets are combined under some operation, how do error costs and attributes accumulate?
	\item Partner packet tracking\index{Partner packet tracking}: packets must keep track of the partner packets with which they are intended to undergo joint operations with. This may be achieved with the addition of {\sc Partners} fields in the packet headers, containing an array of their {\sc Message ID}'s.
	\item Operation signalling\index{Operation signalling}: the recipient node of multiple packets undergoing a joint operation must be informed as to what joint operations should be applied. This may be implemented via the addition of a {\sc What Operation} field to the header.
\end{itemize}

>>>>

To accommodate such multi-packet operations, we must add some modifications to the QTCP protocol to handle:
\begin{itemize}
	\item Packet synchronisation\index{Packet synchronisation}: multiple packets subject to joint operations must be time-synchronised upon implementation of the joint operation. This might involve holding one packet in a quantum memory whilst waiting upon another. Thus, the time required to implement the joint operation is bottlenecked by the packet slowest to arrive.
	\item Bookkeeping of costs and attributes\index{Combining costs \& attributes}: when multiple packets are combined under some operation, how do error costs and attributes accumulate?
	\item Partner packet tracking\index{Partner packet tracking}: packets must keep track of the partner packets with which they are intended to undergo joint operations with. This may be achieved with the addition of {\sc Partners} fields in the packet headers, containing an array of their {\sc Message ID}'s.
	\item Operation signalling\index{Operation signalling}: the recipient node of multiple packets undergoing a joint operation must be informed as to what joint operations should be applied. This may be implemented via the addition of a {\sc What Operation} field to the header.
\end{itemize}

### 2017-10-11 Sections/physical_architectures_for_quantum_computing.tex

\comment{These principles can be extended beyond LO to other schemes where entangling gates are inherently non-deterministic or sometimes fail in a heralded manner. E.g hybrid architectures (Sec.~\ref{sec:hybrid}), where a beamsplitter mediates entanglement via which-path erasure, but only sucessfully projects onto an entangled state with probability 1/2.}

@@

To analyze the operation of such a non-deterministic protocol, we begin by defining a vector $\vec{n}_t$ at time $t$, which stores purely classical information. Specifically, the vector tells us how many clusters of every length we have stored in memory (except single qubit clusters, which we assume `come for free'\footnote{As in beer.}). For example, the second element of the vector tell us how many 3-qubit linear clusters we have in our possession.

@@

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{microcluster_snowflake}
\caption{Snowflake micro-cluster comprising a regular tree sturcture, with branching parameter \mbox{$b=3$} and depth \mbox{$d=4$}. Multiple copies of this micro-cluster can be placed side-by-side and fused together via attempting to bond the most outward available qubits from neighbouring clusters. The tree structure allows excess qubits to be `pruned' via their truncs rather than leaves, bypassing the need to measure out every single leftover qubit, as is the case, for example, for $+$-clusters. This reduces the number of required pruning measurements from linear to logarithmic, similarly reducing the accumulation of errors associated with pruned qubits.} \label{fig:snowflake_graph}\index{Snowflake micro-cluster state}
\end{figure}

@@

For an $m$-mode interferometer, and input state,
\begin{align}
\ket\psi_\text{in} = \ket{T_1,\dots,T_m},
\end{align}
where there are $T_i$ photons in the $i$th input mode, the output superposition takes the form,
\begin{align}
\ket\psi_\text{out} = \sum_S \gamma_{S,T} \ket{S_1,\dots,S_m},
\end{align}
where $S$ sums over all possible photon-number configurations at the output, of which there are,
\begin{align}
|S| = \binom{n+m-1}{n},
\end{align}
where there are $n$ photons in total in $m$ modes. It is assumed that,
\begin{align}
m=O(n^2),
\end{align}
which, for large $m$, puts us into the anti-bunched (i.e binary photon-number) regime with high probability\footnote{That is, we are unlikely to observe more than a single photon in any given output mode, placing us into a binary photo-detection regime. This condition has become known as the `bosonic birthday paradox'.}, rendering non-number-resolved photo-detectors sufficient for physical implementation. However, this `no-collision' subspace remains exponentially large,
\begin{align}
|S_\text{no-collision}| = \binom{m}{n}.
\end{align}

@@

While such negative results might be somewhat depressing, it is extremely insightful to understand these regimes, in the interest of avoiding investing excrutiating effort into trying to instead fruitlessly prove that they are hard.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function SimulatePositiveP($\vec{P}$):
\begin{enumerate}
	\item for(m$\in$modes) \{
	\setlength{\itemindent}{0.2in}
	\item Randomly choose a sample $\alpha_m$ from probability density function $P_m(\alpha)$\index{Probablity density function}.
	\setlength{\itemindent}{0in}
		\item \}
		\item Evolve the set of input coherent state samples through the linear optics network,
		\begin{align}
		\vec\beta = U\cdot\vec\alpha.
		\end{align}
	\item for(m$\in$modes) \{
	\setlength{\itemindent}{0.2in}
	\item The probability of measuring $n$ photons in the $m$th mode is given by the distribution,
	\begin{align}
	D_{m,n} &= |\langle\beta_m|n\rangle|^2 \nonumber \\
	&= e^{-|\beta_m|^2} \frac{{\beta_m}^{2n}}{n!}.
	\end{align}
	\item Choose $n$ from this distribution.
	\setlength{\itemindent}{0in}
	\item \}
	\item return($\vec{n}$).
    \item $\Box$
\end{enumerate}}}}
\caption{Efficient classical algorithm for simulating any linear optics sampling problem whose input states have strictly non-negative $P$-functions, with output measured via photon-counting. $\vec{P}$ is the vector of $P$-functions for all modes.} \label{alg:positive_P_sim}
\end{table}

@@

>>>>

\comment{These principles can be extended beyond LO to other schemes where entangling gates are inherently non-deterministic or sometimes fail in a heralded manner. E.g hybrid architectures (Sec.~\ref{sec:hybrid}), where a beamsplitter mediates entanglement via which-path erasure, but only successfully projects onto an entangled state with probability 1/2.}

@@

To analyse the operation of such a non-deterministic protocol, we begin by defining a vector $\vec{n}_t$ at time $t$, which stores purely classical information. Specifically, the vector tells us how many clusters of every length we have stored in memory (except single qubit clusters, which we assume `come for free'\footnote{As in beer.}). For example, the second element of the vector tell us how many 3-qubit linear clusters we have in our possession.

@@

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{microcluster_snowflake}
\caption{Snowflake micro-cluster comprising a regular tree structure, with branching parameter \mbox{$b=3$} and depth \mbox{$d=4$}. Multiple copies of this micro-cluster can be placed side-by-side and fused together via attempting to bond the most outward available qubits from neighbouring clusters. The tree structure allows excess qubits to be `pruned' via their trunks rather than leaves, bypassing the need to measure out every single leftover qubit, as is the case, for example, for $+$-clusters. This reduces the number of required pruning measurements from linear to logarithmic, similarly reducing the accumulation of errors associated with pruned qubits.} \label{fig:snowflake_graph}\index{Snowflake micro-cluster state}
\end{figure}

@@

For an $m$-mode interferometer, and input state,
\begin{align}
\ket\psi_\text{in} = \ket{T_1,\dots,T_m},
\end{align}
where there are $T_i$ photons in the $i$th input mode, the output superposition takes the form,
\begin{align}
\ket\psi_\text{out} = \sum_S \gamma_{S,T} \ket{S_1,\dots,S_m},
\end{align}
where $S$ sums over all possible photon-number configurations at the output, of which there are,
\begin{align}
|S| = \binom{n+m-1}{n},
\end{align}
where there are $n$ photons in total in $m$ modes. It is assumed that,
\begin{align}
m=O(n^2),
\end{align}
which, for large $m$, puts us into the anti-bunched (i.e binary photon-number) regime with high probability\footnote{That is, we are unlikely to observe more than a single photon in any given output mode, placing us into a binary photo-detection regime. This condition has become known as the `bosonic birthday paradox' \cite{aaronson}.}, rendering non-number-resolved photo-detectors sufficient for physical implementation. However, this `no-collision' subspace remains exponentially large,
\begin{align}
|S_\text{no-collision}| = \binom{m}{n}.
\end{align}

@@

While such negative results might be somewhat depressing, it is extremely insightful to understand these regimes, in the interest of avoiding investing excruciating effort into trying to instead fruitlessly prove that they are hard.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{ 
function SimulatePositiveP($\vec{P}$):
\begin{enumerate}
	\item for(m$\in$modes) \{
	\setlength{\itemindent}{0.2in}
	\item Randomly choose a sample $\alpha_m$ from probability density function $P_m(\alpha)$\index{Probability density function}.
	\setlength{\itemindent}{0in}
		\item \}
		\item Evolve the set of input coherent state samples through the linear optics network,
		\begin{align}
		\vec\beta = U\cdot\vec\alpha.
		\end{align}
	\item for(m$\in$modes) \{
	\setlength{\itemindent}{0.2in}
	\item The probability of measuring $n$ photons in the $m$th mode is given by the distribution,
	\begin{align}
	D_{m,n} &= |\langle\beta_m|n\rangle|^2 \nonumber \\
	&= e^{-|\beta_m|^2} \frac{{\beta_m}^{2n}}{n!}.
	\end{align}
	\item Choose $n$ from this distribution.
	\setlength{\itemindent}{0in}
	\item \}
	\item return($\vec{n}$).
    \item $\Box$
\end{enumerate}}}}
\caption{Efficient classical algorithm for simulating any linear optics sampling problem whose input states have strictly non-negative $P$-functions, with output measured via photon-counting. $\vec{P}$ is the vector of $P$-functions for all modes.} \label{alg:positive_P_sim}
\end{table}

@@

\comment{Add fig for classical vs quantum discrete-time walk}

### 2017-10-11 Sections/quantum_algorithms.tex
Added genetic medicine
Molecular hamiltonians

The algorithm implementing the Deutsch-Jozsa protocol and its circuit diagram are shown in Alg.~\ref{alg:deutsch_jozsa}. The engine room of the algorithm is in the Hadamard transform\index{Hadamard transform}, which prepares an equal superposition of all $2^n$ possible input bit-strings $x$, which are then evaluated in superposition by the oracle. To ensure unitarity, the oracle is defined to implement the transformation,
\begin{align}
	    \hat{U}_f \ket{x}\ket{y} &= \ket{x}\ket{y\oplus f(x)}.
\end{align}
That is, it flips bit $y$ if \mbox{$f(x)=1$}, equivalently addition modula 2 or an XOR operation. An inverse Hadamard transform subsequently yields a measurement outcome with one of two possibilities:
\begin{itemize}
	\item The 0 and 1 terms outputted from the oracle interfere perfectly constructively, if the function was uniform.
	\item They interfere perfectly destructively, if the function was balanced.
\end{itemize}
Then, with a single-shot measurement of the inverse Hadamard transformed output from the oracle we establish whether $f(x)$ was balanced or uniform with certainty. This exhibits an exponential worst case speedup compared to a randomised classical sampling algorithm (which is classically optimal).

@@

We then apply a Grover search repeatedly, each time incrementing this threshold until the algorithm outputs no. Then we know that the last input had the highest score. The reason this approach is \textit{approximate} rather than \textit{exact} is that defining such a score-oracle mightent be always efficiently implemented, or maybe it mightent make sense at all to define score measures for a given problem.

@@

\subsection{Quantum simulation} \index{Quantum simulation}

>>>>

The algorithm implementing the Deutsch-Jozsa protocol and its circuit diagram are shown in Alg.~\ref{alg:deutsch_jozsa}. The engine room of the algorithm is in the Hadamard transform\index{Hadamard transform}, which prepares an equal superposition of all $2^n$ possible input bit-strings $x$, which are then evaluated in superposition by the oracle. To ensure unitarity, the oracle is defined to implement the transformation,
\begin{align}
	    \hat{U}_f \ket{x}\ket{y} &= \ket{x}\ket{y\oplus f(x)}.
\end{align}
That is, it flips bit $y$ if \mbox{$f(x)=1$}, equivalently addition modulo 2 or an XOR operation. An inverse Hadamard transform subsequently yields a measurement outcome with one of two possibilities:
\begin{itemize}
	\item The 0 and 1 terms outputted from the oracle interfere perfectly constructively, if the function was uniform.
	\item They interfere perfectly destructively, if the function was balanced.
\end{itemize}
Then, with a single-shot measurement of the inverse Hadamard transformed output from the oracle we establish whether $f(x)$ was balanced or uniform with certainty. This exhibits an exponential worst case speedup compared to a randomised classical sampling algorithm (which is classically optimal).

@@

We then apply a Grover search repeatedly, each time incrementing this threshold until the algorithm outputs no. Then we know that the last input had the highest score. The reason this approach is \textit{approximate} rather than \textit{exact} is that defining such a score-oracle mightn't be always efficiently implemented, or maybe it mightn't make sense at all to define score measures for a given problem.

@@

\subsection{Quantum simulation} \index{Quantum simulation}\index{Hamiltonian simulation}\label{sec:quantum_sim_alg}

### 2017-10-11 Sections/quantum_error_correction.tex

As discussed previously in Sec.~\ref{sec:QOS}\index{Quality of service}, quality of service is a major consideration in any quantum network. If we are transmitting quantum states over a quantum channel, there will inevitably be deterioration in the form of decoherence, loss, and other undesireable effects we wish to mitigate. In this section we review some of the essential quantum error correction (QEC) techniques that can be used to achieve this.

@@

@@

\comment{Tree horticultural schemere Rudolph et al.}

>>>>

As discussed previously in Sec.~\ref{sec:QOS}\index{Quality of service}, quality of service is a major consideration in any quantum network. If we are transmitting quantum states over a quantum channel, there will inevitably be deterioration in the form of decoherence, loss, and other undesirable effects we wish to mitigate. In this section we review some of the essential quantum error correction (QEC) techniques that can be used to achieve this.

@@

\comment{Add figure}

@@

\comment{Tree horticultural scheme Rudolph et al.}
